Contribution Title\thanks{Supported by organization x.}

### 2019-10-21 paper/paper.tex
Most major parts of dynamic are done

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
%% \usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%%                         %% http://ctan.org/pkg/subcaption
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,automata,calc}
\usepackage{tikz-qtree} % Used for syntax trees
\usepackage{tikz-cd} % Used for commutative diagrams

@@

\newcommand{\basic}{\mathit{basic}} % go from a w \in L(G'_w) to the first element of \alt(w).
\newcommand{\rangebag}{\mathit{rangebag}} % go from a w \in L(G'_w) to the first element of \alt(w).
\newcommand{\rangeset}{\mathit{rangeset}} % go from a w \in L(G'_w) to the first element of \alt(w).
\newcommand{\altset}{\mathit{altset}} % go from a w \in L(G'_w) to \alt(w), except the second element is replaced by a set (that contains an element if the bag contained at least one of that element).
\newcommand{\lattice}{\mathit{lattice}} % go from a t \in L(G_t) to its lattice, partitioned by equality on \altset and ordered by subset on the rangeset.
\newcommand{\topw}{\top_w} % go from a tree to its top word
\newcommand{\botw}{\bot_w} % go from a tree to its bottom word
\newcommand{\localize}{\mathit{localize}} % go from a F \subseteq L(G_t) to a set of localized ambiguities, i.e., a set of subforests.
\newcommand{\range}[2]{#1\!-\!#2}
\newcommand{\regex}{\mathit{Reg}}
\newcommand{\reqpl}{(}
\newcommand{\reqpr}{)}
\newcommand{\reqp}[1]{\reqpl#1\reqpr}
\newcommand{\pospl}{[}
\newcommand{\pospr}{]}
\newcommand{\posp}[1]{\pospl#1\pospr}
\newcommand{\dfa}{\mathit{dfa}} % Go from label to its corresponding dfa
\newcommand{\passthrough}{\mathit{passthrough}} % Go from label to a set of (label x bool), where each element denotes a child production that can be an only child (i.e., no other terminals whatsoever), and the bool states whether it requires parentheses
\newcommand{\labelnt}{\mathit{nt}} % Go from label to the non-terminal to which that labelled production belongs
\newcommand{\labelregex}{\mathit{regex}} % Go from label the regex of the production with that label
\newcommand{\treetorun}{\mathit{run}}
\newcommand{\runtotree}{\mathit{tree}}
\newcommand{\runtoword}{\mathit{word}}
\newcommand{\runprimetorun}{\mathit{normalrun}}

@@

\begin{verbatim}
Proc(T)
  let R = \emptyset
  let U = \emptyset
  for t \in T
    let T' = T \setminus \{t\}
    let A = \words(t)
    loop
      A = A \setminus \bigcup_{t' \in T'} \words(t')
      if L(A) = \emptyset
        U = U \cup \{t\}
        break loop
      if \parse(\shortest(A)) = \{t\}
        R = R \cup \{(t, \shortest(A))\}
        break loop
      T' = \parse(\shortest(A)) \setminus \{t\}
  return (R, U)
\end{verbatim}

>>>>

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
%% \usepackage{subcaption} %% For complex figures with subfigures/subcaptions
%%                         %% http://ctan.org/pkg/subcaption
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,automata,calc}
\usepackage{tikz-qtree} % Used for syntax trees
\usepackage{tikz-cd} % Used for commutative diagrams
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\newcommand{\basic}{\mathit{basic}} % go from a w \in L(G'_w) to the first element of \alt(w).
\newcommand{\rangebag}{\mathit{rangebag}} % go from a w \in L(G'_w) to the first element of \alt(w).
\newcommand{\rangeset}{\mathit{rangeset}} % go from a w \in L(G'_w) to the first element of \alt(w).
\newcommand{\altset}{\mathit{altset}} % go from a w \in L(G'_w) to \alt(w), except the second element is replaced by a set (that contains an element if the bag contained at least one of that element).
\newcommand{\lattice}{\mathit{lattice}} % go from a t \in L(G_t) to its lattice, partitioned by equality on \altset and ordered by subset on the rangeset.
\newcommand{\topw}{\top_w} % go from a tree to its top word
\newcommand{\botw}{\bot_w} % go from a tree to its bottom word
\newcommand{\localize}{\mathit{localize}} % go from a F \subseteq L(G_t) to a set of localized ambiguities, i.e., a set of subforests.
\newcommand{\range}[2]{#1\!-\!#2}
\newcommand{\regex}{\mathit{Reg}}
\newcommand{\reqpl}{(}
\newcommand{\reqpr}{)}
\newcommand{\reqp}[1]{\reqpl#1\reqpr}
\newcommand{\pospl}{[}
\newcommand{\pospr}{]}
\newcommand{\posp}[1]{\pospl#1\pospr}
\newcommand{\dfa}{\mathit{dfa}} % Go from label to its corresponding dfa
\newcommand{\passthrough}{\mathit{passthrough}} % Go from label to a set of (label x bool), where each element denotes a child production that can be an only child (i.e., no other terminals whatsoever), and the bool states whether it requires parentheses
\newcommand{\labelnt}{\mathit{nt}} % Go from label to the non-terminal to which that labelled production belongs
\newcommand{\labelregex}{\mathit{regex}} % Go from label the regex of the production with that label
\newcommand{\treetorun}{\mathit{run}}
\newcommand{\runtotree}{\mathit{tree}}
\newcommand{\runtoword}{\mathit{word}}
\newcommand{\runprimetorun}{\mathit{normalrun}}
\newcommand{\shortest}{\mathit{shortest}}

@@

\begin{algorithm}
\caption{The Dynamic Algorithm}
\begin{algorithmic}[1]
\Procedure{Dynamic}{$T$}
  \State $R <- \emptyset$
  \State $U <- \emptyset$
  \ForAll{$t \in T$}
    \State $T' <- T \setminus \{t\}$
    \State $A <- \words(t)$ \Comment{$A$ is a visibly pushdown automaton.}
    \Loop
      \State $A <- A \setminus \bigcup_{t' \in T'} \words(t')$ \Comment{VPDAs closed under difference and union.}
      \If{$L(A) = \emptyset$}
        \State $U <- U \cup \{t\}$
        \State $\textbf{break loop}$
      \EndIf
      \If{$\parse(\shortest(A)) = \{t\}$} \Comment{$\shortest(A)$ denotes a shortest}
        \State $R <- R \cup \{(t, \shortest(A))\}$ \Comment{word recognized by $A$.}
        \State $\textbf{break loop}$
      \EndIf
      \State $T' <- \parse(\shortest(A)) \setminus \{t\}$
    \EndLoop
  \EndFor
  \State $\textbf{return} (R, U)$
\EndProcedure
\end{algorithmic}
\end{algorithm}
